---
title: "8867_Homework7_110122"
output: html_document
date: "2022-11-01"
---

In the file TV.txt is a correlation matrix of how much respondents “really like to watch” the 10 TV programs: Professional Boxing(s), This Week, Today, World of Sport(s), Grandstand(s), Line-Up, Match of the Day(s), Panorama, Rugby Special(s), 24 Hours, where those marked with * are sport programs and the remaining are news programs. The sample size is quite large, but here we use  sample size 200 just for demonstrative purpose. 

```{r}
#load dataset
tv_R <- read.table('TV.txt')
tv_R <- as.matrix(tv_cor, rownames = FALSE)

# add column names
tv_names <- list("prof_box", "this_week", "today", "world_sports", "grandstands", "line-up", "match_day", "panorama", "rugby", "24")

colnames(tv_R) <- c(tv_names)
rownames(tv_R) <- c(tv_names)

tv_R
```

**Q1. Create a screeplot and run parallel analysis (use 1, 000 replications, add error bars, and use 95th percentile for decision). What are the conclusions from screeplot and from parallel analysis?** 

```{r}
library(psych)

# run paralell analysis
fa.parallel(tv_R, fa = "pc", n.iter = 1000, error.bars = TRUE)
```


**Q2. Run PCA and retain 2 PCs, use an oblique target rotation. What is a proper target given the background of the 10 programs? What are the interpretation of the 2 components?** 

```{r}
# run PCA
result.quartimin <- principal(tv_cor, 2, rotate = "quartimin")

# extract loadings
result.quartimin$loadings

#extract weights
result.quartimin$weights

#extract structural matrix
result.quartimin$Structure
```

```{r}
# create target
## PC1 - sports (1, 4, 5,7, 9)
## PC2 - news (2, 3, 6, 8,10 )

target <- make.keys(10, list(PC1 = c(1, 4, 5, 7, 9), PC2 = c(2, 3, 6, 8, 10)))
target <- scrub(target, isvalue=1)
rownames(target) <- tv_names

target

# target rotation
result.target <- principal(tv_cor, 2, rotate = "targetQ", Target = target)
result.target

# extract loadings
result.target$loadings

#extract weights
result.target$weights

#extract structural matrix
result.target$Structure
```

A logical target it to split the components by category: sports programs and news. 

The interpretation of the 2 components ...

**Q3.	What proportion of total variance in the original variables is explained by the two components (as a whole)? At the individual level, which TV program has the largest proportion of variance  explained by the two PCs (and how much)? Which has the least (and how much)?** 

```{r}
# SS of loadings - column-wise sum of squared loadings = eigenvalues (variance explained) in unrotated loadings

    # sum of square loadings at the 0 locations of the target for 
    # target rotated solution

    sum(result.target$loadings[!is.na(target[,2:1])]^2)

# Prop Var - proportion of variance explained out of total variance of 10, number of variables

# communality (h2) - proprtion of variance in program explained by the two PCs
```

The proportion of total variance in the original variables explained by the two components is [x]
The TV program with the largest proportion of variance explained by the two PCs is [], with a communality = [x]
The TV program with the lowest proportion of variance explained by the two PCs is [], with a communality = [x]

**Q4.	How much variance do the two PCs share with each other?** 
```{r}
# correlation between 2 components 
result.target$Phi

    # if correlation is 0.3, two PCs share about 9% of variance
```

The two PCs share [x %] of variance. 

**Q5.	Express the PC1 in terms of the original standardize variables.** 

y1 = ()x1 + ()x2 + ()x3 + ()x4 + ()x5 + ()x6 + ()x7 + ()x8 + ()x9 + ()x10

**Q6.	Write a regression equation that regresses Boxing on the two PCs.** 

y1 = ()x1 + ()x2 + ()x3 + ()x4 + ()x5 + ()x6 + ()x7 + ()x8 + ()x9 + ()x10

y2 = ()x1 + ()x2 + ()x3 + ()x4 + ()x5 + ()x6 + ()x7 + ()x8 + ()x9 + ()x10

x1(boxing) = ()y1 + ()y2 + e1

**Q7.	What is the correlation between World Sport and PC1?** 
```{r}

```

