
```{r}
bsas <- read.table('BSASgovern.dat')
clep <- read.table('CLEP.dat')
```

```{r}
```

### Q1 ###

In the file ’BSASgovern.dat’ are ratings from 786 respondents to the following 
five questions on the 1996 British Social Attitudes Survey: on the whole do you 
think it should or should not be the government’s responsibility to:
  
    - provide a job for everyone who wants one,
    - keep prices under control
    - provide a decent standard of living for the unemployed 
    - reduce income differences between the rich and the poor
    - provide decent housing for those who can’t afford it.

Response alternatives are: 1=definitely should be; 2=probably should be; 
3=probably should not be; 4=definitely should not be.

### Q1.1 ###

Obtain the polychoric correlation matrix and thresholds.

```{r}

```

### Q1.2 ###

Show how the thresholds of the first item can be calculated through the function qnorm. You can use the function table to obtain counts of the four categories.

```{r}

```

### Q1.3 ###

Calculate Pearson correlation matrix from the five ordered categorical variables directly, and compare to the polychoric correlation matrix. What do you observe?

```{r}

```

### Q2 ###

In the file CLEP.dat are scores on Social science and history, Verbal, and Science of 87 subjects. 

### Q2.1 ###

Find the means, covariance matrix and correlation matrix of the three variables.

### Q2.2 ###

Obtain histogram and QQplot (against normal distribution) for each of the variables. Add a line to the plots. For variable Verbal, explain how you infer the skewness of this variable from its QQplot.

### Q2.3 ###

Do Shapiro-Wilk test with each variable and obtain p-values. Draw conclusion based on Holm’s procedure.

### Q2.4 ###

Calculate the squared Mahalanobis distance d2 for each case in this sample. Report the case number associated with the largest d2. Do NOT remove.

### Q2.5 ###

Obtain a QQplot for d2 and add a reference line to the plot. What reference distribution should you use?

### Q2.6 ###

Do Shapiro-Wilk test for the d2. Draw conclusion.
