---
title: "PSYGS8867_Homework9"
output: html_document
date: "2022-11-17"
---
The data set UScitiesD (in R base) contains distances among 10 U.S. cities.

```{r}
data <- as.matrix(UScitiesD)
```

### 1 Run classical MDS and plot the eigenvalues. How many dimensions does the plot recommend?

```{r}
result <- cmdscale(data, k=2, eig=TRUE)
plot(result$eig)
abline(h=0)
```
The plot suggests 2 dimensions.

### 2 Plot the solution for two dimensions. How is it related to the actual map of the U.S.?

```{r}
plot(result$points,asp = 1,ylim=c(-2000,2000))
text(result$points[,1],result$points[,2],labels=rownames(result$points),cex=.7,pos=2)
```
This map is similar to a map of the US except that is flipped both vertically and horizontally. 

```{r}
points<-result$points
points[,2]<- -points[,2]
plot(points,asp = 1,ylim=c(-2000,2000))
text(points[,1],points[,2],labels=rownames(points),cex=.7,pos=2)
```
After rotating the map is now only flipped horizontally. 

### 3. Show how the two GOF values in the solution can be calculated from the eigenvalues.

```{r}
#GOF values in solution
result$GOF
```

```{r}
#The first GOF takes the absolute values of the negative eigenvalues in its calculation

eig <- result$eig
eig_abs <- abs(eig)
eig_abs

#The second GOF treats eigenvalues as 0
eig_0 <- replace(eig, 7:10, 0)
eig_0
```

```{r}
#GOF = proportion of total eigenvalues retained by two dimensions
GOF1 <- (eig_abs[1] + eig_abs[2]) / (eig_abs[1] + eig_abs[2] + eig_abs[3] + eig_abs[4] + eig_abs[5] + eig_abs[6] + eig_abs[7] + eig_abs[8] + eig_abs[9] + eig_abs[10])
GOF1

GOF2 <- (eig_0[1] + eig_0[2]) / (eig_0[1] + eig_0[2] + eig_0[3] + eig_0[4] + eig_0[5] + eig_0[6] + eig_0[7] + eig_0[8] + eig_0[9] + eig_0[10])
GOF2
```

