---
title: "8880_HW3"
output: html_document
date: "2023-03-01"
---
#Set up
```{r}
## Call libraries eRm, ltm, and mirt
library(eRm)
library(ltm)
library(mirt)
```

```{r}
## Importing polytomous data (polytomous.txt)
poly <- read.table("Lab 3/polytomous.txt",header=TRUE)
poly[1:10,1:10] # Checking the first 10 rows and 10 columns
```

#Q1
Report item parameter estimates and standard errors of a graded response model

```{r}
## Fitting a graded response model using 'mirt'
# Item parameters
 
grm <- mirt(poly, 1, itemtype='graded', method="EM", SE=TRUE)
coef.grm <-coef(grm, printSE=TRUE, as.data.frame=TRUE)
coef.grm
```

#Q2 
Create and interpret item characteristic curves (ICCs) for a graded response model for three items habing distinct patterns

```{r}
# CCC
itemplot(grm, 1) #CCC for item 1
```

#Q3
Compare a target information curve you designed with test information curve from your real responses for a graded response model.

```{r}
# Item & test Information functions
plot(grm, type = 'info') #test information for all items
```

#Q4
Discuss the differences of the item location estimates between a general partial credit model and a graded response model

```{r}
## Fitting a graded response model using 'mirt'
# Item parameters
 
grm <- mirt(poly, 1, itemtype='graded', method="EM", SE=TRUE)
coef.grm <-coef(grm, printSE=TRUE, as.data.frame=TRUE)
Coef.grm
```

```{r}
## Fitting a generalized partial credit model using 'ltm': Marginal MLE
# Item parameters
gpcm <- gpcm(poly, IRT.param = TRUE)
summary(gpcm)
```

